\cvsection{Research Experience}

\begin{cventries}

\cventry
    {Graduate Researcher} % Job title
    {CORE Robotics Lab at Georgia Tech} % Organization
    {Atlanta, GA} % Location
    {August 2022 - August 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working under Dr. Matthew Gombolay in the CORE Robotics lab}
        \item {Submitted a paper to Robotics: State and Society on the efficacy of having non-experts provide demonstrations to to teach robots via LfD. Conducted a user study with over 30 participants and observed how they taught the robot.}
        \item Paper name: \textcolor{awesome}{\underline{\href{https://openreview.net/forum?id=kXy0HAnah0-}{Investigating the Impact of Experience on a User's Ability to Perform Hierarchical Abstraction}}}
        \item {Programmed a Kinova MOVO robot to serve dementia patients in a hospice setting. Robot observes and plans in environment via ROS, computer vision, and deterministic planning.}
      \end{cvitems}
    }
\cventry
    {Graduate Research Assistant} % Job title
    {Georgia Tech Research Institute} % Organization
    {Atlanta, GA} % Location
    {January - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing an app ClarityNLP that is used by clinical researchers to build and run patient phenotypes using structured and unstructured data.}
        \item {Developed NLP and regex algorithms to parse hospital documents and used PostGreSQL and internal APIs to allow comparisons and archival.}
      \end{cvitems}
    }
\cventry
    {Undergraduate Researcher} % Job title
    {Vertically Integrated Projects: Big Data and Quantum Mechanics} % Organization
    {Atlanta, GA} % Location
    {January 6, 2020 - May 8, 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized machine learning to enable faster and more accurate calculations of the quantum mechanical properties of chemical reactions}
        \item {Used Atomic Simulation Environment (ASE) to simulate atoms in certain positions and energy levels and used a variety of machine learning algorithms to train on these simulations.}
        \item {Contributed to hyperparameter optimization to maximize the capabilities of our convolution neural net (PyTorch), used HyperOpt to improve performance.}
      \end{cvitems}
    }

\end{cventries}
