\cvsection{Experience}

\begin{cventries}

\cventry
    {Machine Learning Developer} % Job title
    {Edaptive Computing} % Organization
    {Remote} % Location
    {February 2024 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilizing transformer models and Large Language Models (LLMs) in an NLP Server to process large, unstructured documents for various uses.}
        \item {Using and finetuning (using LoRA) Llama LLMs to process and store docs and build a RAG chatbot to accuately answer questions from the docs.}
        \item {Utilizing embedding models to store text with metadata from uploaded docs in vector databases for similarity search and RAG capabilities.}
        \item {Implementing spaCy and NLTK to check for grammatical, syntactical, and vocabulary inconsistencies, given a specifical required style}
        \item {Building production-ready builds using TensorRT, llama.cpp, RabbitMQ, gevent/gunicorn, node.js, Docker, and Flask after prototyping with PyTorch and Huggingface.}
      \end{cvitems}
    }
    
\cventry
    {AI Researcher} % Job title
    {Defense Research Associates} % Organization
    {Beavercreek, OH} % Location
    {August 2023 - February 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched how to use LLMs solve math problems, such as finetuning with unique tokenizations}
        \item {Brainstormed ways to detect, identify, and track unknown objects in the sky from a video using Vision Transformers (ViT), Graph Neural Networks (GNNs), Reinforcement Learning (PPO), Convolutional Neural Nets (CNNs), and Kalman Filters.}
      \end{cvitems}
    }

\cventry
    {Graduate Researcher} % Job title
    {CORE Robotics Lab at Georgia Tech} % Organization
    {Atlanta, GA} % Location
    {August 2022 - August 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working under Dr. Matthew Gombolay in the CORE Robotics lab while obtaining my MS CS at Georgia Tech}
        \item {Published a paper at RSS on the efficacy of non-expert demonstrations to teach robots via Learning from Demonstration (LfD)}
        \item {Programmed a Kinova MOVO robot to serve dementia patients in a hospice setting. Robot observes and plans in environment via ROS, computer vision, and deterministic planning.}
      \end{cvitems}
    }

\cventry
    {Data Analyst Intern} % Job title
    {Symbotic} % Organization
    {Wilmington, MA} % Location
    {May 2022 - August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed thousands of bot data logs to preemptively detect, pinpoint, and prevent 99\% of charger faults using Python, Pandas, and Tableau.}
      \end{cvitems}
    }

%   \cventry
%     {Full stack Software Engineering Intern} % Job title
%     {Chatham Financial} % Organization
%     {Remote} % Location
%     {June 2021 - August 2021} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Created an app using .NET Core MVC Services that pulls data from internal gRPC services and external APIs to process swap option volatilities}
%         \item {Developed frontend capabilities using React/Redux to display and visualize market data in a 3D plot using Plotly.js}
%       \end{cvitems}
%     }

\end{cventries}
